Gut microbes and their genes are associated with cognition and neuroanatomy in children

### 2023-03-25 manuscript/main.tex

Prediction of cognitive scores was carried out as a set of regression
experiments targeting real-valued continuous assessment scores.
Different experiment sets were designed to probe how different
representations of the gut microbiome (taxonomic profiles, Functional
profiles encoded as ECs) would behave, with and without the addition of
demographics (sex and maternal education as a proxy of socioeconomic
status) on participants from different age groups. Age (in months) was
provided as a covariate for all models (Table 5).

\textbf{Table 5. Experimental design and input composition for Random
Forest experiments}

\begin{table}
    \begin{tabular}{|r|r|r|r|}
      \hline\hline
      \textbf{Input set} & \textbf{Age bracket} & \textbf{Microbiome encoding type} & \textbf{Demographics Provided? (sex, education)} \\\hline
      1 & \multirow{5}{*}{0 to 6 months} & Not provided & yes \\ \cline{3-4}
      2 &  & \multirow{2}{*}{Taxonomic profile} & no \\ \cline{4-4}
      3 &  &  & yes \\ \cline{3-4}
      4 &  & \multirow{2}{*}{Functional Profile (ECs)} & no \\ \cline{4-4}
      5 &  &  & yes \\ \cline{2-4}
      6 & \multirow{5}{*}{18 to 120 months} & Not provided & yes \\ \cline{3-4}
      7 &  & \multirow{2}{*}{Taxonomic profile} & no \\ \cline{4-4}
      8 &  &  & yes \\ \cline{3-4}
      9 &  & \multirow{2}{*}{Functional Profile (ECs)} & no \\ \cline{4-4}
      10 &  &  & yes \\\hline\hline
    \end{tabular}
\end{table}

>>>>

Prediction of cognitive scores was carried out as a set of regression
experiments targeting real-valued continuous assessment scores.
Different experiment sets were designed to probe how different
representations of the gut microbiome (taxonomic profiles, Functional
profiles encoded as ECs) would behave, with and without the addition of
demographics (sex and maternal education as a proxy of socioeconomic
status) on participants from different age groups. Age (in months) was
provided as a covariate for all models (Table S3).
